### 2020-07-29 theory/notes_banks_buyingfinitemajorities.tex
incorporate additional notes on banks

\documentclass[12pt,a4paper]{article}
\usepackage{setspace} \onehalfspacing
\usepackage[top = 1in, bottom = 1in, left = 1in, right = 1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{float}
\usepackage{pdflscape}
\usepackage{booktabs}
\usepackage{dcolumn}
\usepackage{pdflscape}
\usepackage[hyphens]{url}
\usepackage{enumitem}
\usepackage[table]{xcolor}
\usepackage{authblk}
\usepackage{appendix}
\usepackage{titletoc}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}{Proposition}
\renewcommand{\theproposition}{\arabic{proposition}}
\newtheorem{corollary}[theorem]{Corollary}
\newcommand{\real}{\mathbb{R}_+^n}

@@

>>>>

\documentclass[12pt,a4paper]{article}
\usepackage{setspace} \onehalfspacing
\usepackage[top = 1.25in, bottom = 1.25in, left = 1.25in, right = 1.25in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{float}
\usepackage{pdflscape}
\usepackage{booktabs}
\usepackage{dcolumn}
\usepackage{pdflscape}
\usepackage[hyphens]{url}
\usepackage{enumitem}
\usepackage[table]{xcolor}
\usepackage{authblk}
\usepackage{appendix}
\usepackage{titletoc}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\renewcommand{\theproposition}{\arabic{proposition}}
\newcommand{\real}{\mathbb{R}_+^n}

@@

The "convexity" of $E$ guarantees that local information is sufficient to generate comparative statistics regarding changes in preferences $\mathbf{v}' \rightarrow \mathbf{v}$. Here, this local information is summarized by the preferences of the marginal voter $v_k$ and non-bribed voter $v_{k + 1}$. In order to identify these voters, one needs to solve for the optimal coalition size. Instead, Banks takes an alternative route and characterizes a weaker comparative statistic result which holds globally. Given two preferences $\mathbf{v}$ and $\mathbf{v}'$, write $\mathbf{v}$ and $\mathbf{v}'$, write $\mathbf{v} \geq \mathbf{v}'$ if $v_i \geq v'_i$ for all $i \in N$.

\begin{corollary}
    \label{cor:change_k}
    For all $\mathrm{W_B}$, if $\mathbf{v} \geq \mathbf{v}'$ then $\mathrm{k}^*(\mathbf{v}, \mathrm{W_B}) \geq \mathrm{k}^*(v', \mathrm{W_B})$
\end{corollary}

Thus, the optimal number of voters bribed by $A$ and hence the optimal size of $A$'s optimal coalition, weakly increases as voters find $A$'s preferred alternative, $x$, more attractive. Although $A$'s total expenditure will decrease as $x$ becomes more attractive to the legislature, the optimal way to allocate this lower amount is to spread it more widely among voters.

We can also characterize the change in total expenditures as a result of a shift in voter preferences. From equation \ref{eqn:total_expenditure} we have

\begin{align*}
    E(k, \mathbf{v}, W_B) - E(k, \mathbf{v}', W_B) & = \\
    &= k \cdot t(k, W_B) - \sum_{i \leq k} v_i - \left[k \cdot t(k, W_B) - \sum_{i \leq k} v'_i\right]\\
    &= \sum_{i \leq k}(v'_i - v_i)
\end{align*}

Since $v_i - v'_i \geq 0$, the difference in expenditure between a more favorable and unfavorable legislature is always non-positive.
